Local Point Spread Function Approximation of High-Rank Hessians in Inverse Problems Governed by PDEs\thanks{Research supported partially by NSF-DMS-CAREER-1654311 and NSF-OAC-1550547.}

### 2024-03-01 presentations/siampp24-tucker/localpsf_revised_figures/frog_tau_impulses.tex
adding files for my SIAM PP24 talk

\begin{document}
	\begin{tikzpicture}[baseline]%, trim axis right]
		\begin{axis}[width=0.49\linewidth, height=0.5\linewidth,
		xmode=log,
		ymode=log,
		ymin=1e-4,
		ymax=1e0,
%		xmax=1000,
		axis x line*=bottom,
		axis y line*=left,
%		xtick={0, 200, 400, 600,800,1000},
		xlabel={\#impulse responses},
		ylabel={$\|\boldsymbol{\Phi} - \widetilde{\boldsymbol{\Phi}}\|_\text{Fro} / \|\boldsymbol{\Phi}\|_\text{Fro}$},
		title={PSF convergence (impulse responses)},
		legend style={at={(1.2,1)},anchor=north east,draw=none},
		legend pos=south west,
		legend style={font=\small}
		]
			\addlegendentry{$\tau=2.0$}
			\addplot[black, line width=0.5mm] table {frog_convergence_impulses_tau2.0.dat};
			\addlegendentry{$\tau=2.5$}
			\addplot[blue, line width=0.5mm] table {frog_convergence_impulses_tau2.5.dat};
			\addlegendentry{$\tau=3.0$}
			\addplot[cyan, line width=0.5mm] table {frog_convergence_impulses_tau3.0.dat};
			\addlegendentry{$\tau=3.5$}
			\addplot[purple, line width=0.5mm] table {frog_convergence_impulses_tau3.5.dat};
			\addlegendentry{$\tau=4.0$}
			\addplot[red, line width=0.5mm] table {frog_convergence_impulses_tau4.0.dat};
		\end{axis}
	\end{tikzpicture}
\end{document}

>>>>

\begin{document}
	\begin{tikzpicture}[baseline]%, trim axis right]
		\begin{axis}[width=0.49\linewidth, height=0.5\linewidth,
		xmode=log,
		ymode=log,
		ymin=1e-4,
		ymax=1e0,
%		xmax=1000,
		axis x line*=bottom,
		axis y line*=left,
%		xtick={0, 200, 400, 600,800,1000},
		xlabel={\#impulse responses},
		ylabel={$\|\boldsymbol{\Phi} - \widetilde{\boldsymbol{\Phi}}\|_\text{Fro} / \|\boldsymbol{\Phi}\|_\text{Fro}$},
		title={PSF convergence (impulse responses)},
		legend style={at={(0.5,0.5)},anchor=north east,draw=none},
%		legend pos=south west,
		legend style={font=\small,fill=none}
		]
			\addlegendentry{$\tau=2.0$}
			\addplot[olive, line width=0.5mm] table {frog_convergence_impulses_tau2.0.dat};
			\addlegendentry{$\tau=2.5$}
			\addplot[blue, line width=0.5mm] table {frog_convergence_impulses_tau2.5.dat};
			\addlegendentry{$\tau=3.0$}
			\addplot[cyan, line width=0.5mm] table {frog_convergence_impulses_tau3.0.dat};
			\addlegendentry{$\tau=3.5$}
			\addplot[black, line width=0.5mm] table {frog_convergence_impulses_tau3.5.dat};
			\addlegendentry{$\tau=4.0$}
			\addplot[red, line width=0.5mm] table {frog_convergence_impulses_tau4.0.dat};
%			\addlegendentry{$\text{const} \times \left(\# \text{impulse responses}\right)$}
			\addplot[dashed, color=gray, line width=0.5mm] table {frog_convergence_rate_impulses.dat};
		\end{axis}
	\end{tikzpicture}
\end{document}
